Human-level control through deep reinforcement learning

### 2018-01-02 article/article.tex
Cite tensorflow

Therefore, the NN is trained by minimizing the Huber loss~\citep{huber1964robust} with $\delta=1$ of the Bellman equation (by a -- stochastic -- gradient descent).
The Huber loss $H_\delta$, parameterized by $\delta \in {\mathbb R^*}^+$, is a continuous function (also $C^1$ but not $C^2$) defined by the MSE
on a small neighbourhood of $0$, and by the absolute value outside this neighbourhood:
\begin{equation}
	H_\delta : \mathbb R \to \mathbb R : x \mapsto \begin{cases}\frac 12x^2                                &\text{ if } \abs x \leq \delta,\\
	                                                            \delta\left(\abs x - \frac 12\delta\right) &\text{ otherwise.}\end{cases}
\end{equation}

@@

>>>>

Therefore, the NN is trained by minimizing the Huber loss~\citep{huber1964robust} with $\delta=1$ of the Bellman equation (by a -- stochastic -- gradient descent).
The Huber loss $H_\delta$, parameterized by $\delta \in {\mathbb R^*}^+$, is a continuous function (also $C^1$ but not $C^2$) defined by the mean
squared error on a small neighbourhood of $0$, and by the absolute value outside this neighbourhood:
\begin{equation}
	H_\delta : \mathbb R \to \mathbb R : x \mapsto \begin{cases}\frac 12x^2                                &\text{ if } \abs x \leq \delta,\\
	                                                            \delta\left(\abs x - \frac 12\delta\right) &\text{ otherwise.}\end{cases}
\end{equation}

@@

\subsubsection{Implementation}
Tensorflow \todo{explain}
\citep{tensorflow2015-whitepaper}
